Untitled Draft

### 2023-03-22 doc/manuscript.Rmd
Made table captions easier to understand. Also fixed capitalisation of PA in figures. Make manuscript use model_tables_age, not model_tables.

```{r load-targets, include=FALSE}
tar_load(model_list_by_age)
tar_load(data_clean)
tar_load(purdy_pictures_by_age)
tar_load(model_tables)
tar_load(demog_table)
pretty <- function(x) format(x, big.mark = ",")
```

@@

```{r sleep-outcomes}
papaja::apa_table(
  model_tables$sleep$data,
  caption = model_tables$sleep$caption,
  note = model_tables$sleep$note,
  col_spanners = model_tables$sleep$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

@@

```{r pa-outcomes}
papaja::apa_table(
  model_tables$physical_activity$data,
  caption = model_tables$physical_activity$caption,
  note = model_tables$physical_activity$note,
  col_spanners = model_tables$physical_activity$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

>>>>

```{r load-targets, include=FALSE}
tar_load(model_list_by_age)
tar_load(data_clean)
tar_load(purdy_pictures_by_age)
tar_load(model_tables_age)
tar_load(demog_table)
pretty <- function(x) format(x, big.mark = ",")

```

@@

```{r sleep-outcomes}
papaja::apa_table(
  model_tables_age$sleep$data,
  caption = model_tables_age$sleep$caption,
  note = model_tables_age$sleep$note,
  col_spanners = model_tables_age$sleep$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

@@

```{r pa-outcomes}
papaja::apa_table(
  model_tables_age$physical_activity$data,
  caption = model_tables_age$physical_activity$caption,
  note = model_tables_age$physical_activity$note,
  col_spanners = model_tables_age$physical_activity$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```
